Recurrence spike spectra

### 2022-07-12 Manuscript/inter_spike_manuscript.tex
Power Grid application prepared

\subsection{Evolutionary spike spectrogram of Earth's orbit time series}

To demonstrate the usefulness of the proposed inter spike spectrum, we apply it to the freely available eccentricity time series of 
\citet{Laskar2011}. \todo[inline]{blabla what is this used for usually? etc.} We use a time series which covers the past \mytilde $67$ Mio. years, which a total length
of $N=13,421$ samples and a sampling period of $\Delta t= 5,000$.

%While in Chapter \ref{chapter:MCDTS}, 
%Section \ref{sec_mcdts_cenogrid_prediction} predictions were made for the detrended $\delta^{13}$C record, here the focus is on the analysis of the characteristic time scales 
%in both, the detrended $\delta^{18}$O and the detrended $\delta^{13}$C isotope records. Specifically, we have computed spike powerspectra of the $\tau$-RR windowed over each record. 
%Figures~\ref{fig_tauRR_O18_pecuzal},~\ref{fig_tauRR_C13_pecuzal} show that major features of their linear counterparts, namely ordinary FFT spectrograms (A panels), are also present in 
%these spectrograms. But there is additional information in the spike spectrograms (B panels). Firstly, overall there seem to be less frequencies excited than in the FFT spectrograms, but these 
%excited frequencies are therefore more pronounced. This is especially apparent in the oxygen isotope record spectrogram (Fig.~\ref{fig_tauRR_O18_pecuzal}), in which the obliquity-related time 
%scale (\mytilde 41 kyrs) is very prominent from 17-0 Mio yrs BP in the spike spectrogram (panel B). Our spike spectrograms also support the general conlusion given by \textcite{Westerhold2020} 
%that ``in the Hothouse and Warmhouse climate states, as well as the first Coolhouse phase, eccentricity-related cycles (\mytilde 100 \& \mytilde 405 kyrs) dominate the CENOGRID records, while 
%after the increasing influence of highlatitude cooling and ice growth during the second Coolhouse phase, the obliquity-band response steadily increases after 13.9 Mio yrs BP (middle Miocene 
%climate transition) before dominating climate dynamics by \mytilde 5 Mio yrs BP (late Miocene–early Pliocene)''. The spike spectrograms indicate a strong obliquity influence already from 17 
%Mio yrs BP (the onset of the Miocene Climate optimum). Moreover, in the carbon isotope record based spike spectrogram (Fig.~\ref{fig_tauRR_C13_pecuzal}B) there is a strong influence of the 
%100-kyr-eccentricity cycle in the first Warmhouse phase from \mytilde 61-56 Mio yrs BP, which is not represented in the FFT-based spectrogram (panel A). 
%
%
%\begin{figure}
% \centering
% \includegraphics[width=\textwidth]{./figures/fig_tauRR_O18_pecuzal}
% \caption{Evolutionary spectrograms based on \textbf{A} FFT powerspectra of the detrended $\delta^{18}$O time series and \textbf{B} 
% on the spike powerspectra of the 
% $\tau$-RR of the PECUZAL embedded $\delta^{18}$O record. The spectrograms were computed with a $w = 1,000 (\hat{=}~\text{5-Myr})$ window 
% and a step $ws=1$. We used the 
% embedding computed in Chapter~\ref{chapter:MCDTS} (Section~\ref{sec_mcdts_cenogrid_prediction}, see Table~\ref{tab:cenogrid_embedding}) 
% and a recurrence threshold fixed to 
% 5\% global RR, in order to ensure comparability within the different windows \cite{kraemer2018} (Chapter~\ref{chapter:threshold}). 
% Dashed red horizontal lines indicate major climate transitions according to \textcite{Westerhold2020}.
% }
%\label{fig_tauRR_O18_pecuzal}
%\end{figure}
%
%\begin{figure}
% \centering
% \includegraphics[width=\textwidth]{./figures/fig_tauRR_C13_pecuzal}
% \caption{Same as in Figure \ref{fig_tauRR_O18_pecuzal}, but for the detrended $\delta^{13}$C isotope record.
% }
%\label{fig_tauRR_C13_pecuzal}
%\end{figure}
%
%The shown spike spectrograms in Figs.~\ref{fig_tauRR_O18_pecuzal},~\ref{fig_tauRR_C13_pecuzal} are based on the $\tau$-RR of the respective records, which have been time delay embedded by using 
%the PECUZAL algorithm \cite{Kraemer2021} (Chapter \ref{chapter:unified}). By construction, we would expect different spike spectrograms, when different embeddings are used. This is indeed the case 
%as shown in Figures~\ref{fig_tauRR_O18_mcdts},~\ref{fig_tauRR_C13_mcdts},~\ref{fig_tauRR_O18_ne},~\ref{fig_tauRR_C13_ne} (Appendix \ref{appendix_tauRR_spectrograms}), which also show spike 
%spectrograms, but for an embedding using MCDTS-R-MSE (Chapter~\ref{chapter:MCDTS}, see Table~\ref{tab:cenogrid_embedding}) and for the non-embedded time series. Even though differences are 
%discernible, the mentioned overall conclusion given by \textcite{Westerhold2020} also holds for these cases.

>>>>

\subsection{Inter spike spectra of power grid frequency data}

lalalalalala
lalalal \\

lalala\\
\begin{figure}
 \centering
 \includegraphics[width=\textwidth]{./figures/fig_power_grid_spectra_lasso_standard_20s}
 \caption{THIS WILL BE A HIGH-RES FIGURE SOON AND A CAPTION WILL BE ADDED  
}
\label{fig_power_spectra_frequency}
\end{figure}
